--- 
title: "Justice Informatics Student Group"
author: "Columbia University DBMI Students"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: adriennepichon/bookdown-JusticeInformatics
description: "Resources and documentation for the Columbia DBMI Justice Informatics Student Group."
---


```{r eval=FALSE}
#This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.
#The **bookdown** package can be installed from CRAN or Github:

install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

```{r include=FALSE}
#Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.
#To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

# Overview
The **Justice Informatics Student Group** was started by a group of PhD students at Columbia University's Department of Biomedical Informatics (DBMI) following the discussions in Summer 2020 about addressing racism in academia. _Details of the group's history, mission, and structure can be found in Chapter \@ref(about)._

Generally, the group selects one book to read each semester (Fall, Spring, Summer) that focuses on justice and technology, data, or research. Students meet weekly to discuss chapters and connect the readings to our own work in informatics and health, with a particular focus on feminist and anti-racist approaches. Faculty will be invited for a broad discussion of the book near the end of each semester.

In addition to discussing chapters from our selected books, we also share and discuss journal articles, podcasts or online lectures, relevant current events and twitter threads, and other related content. Finally, we use this group as a space to discuss racist or hate-driven events and otherwise cultivate a supportive space for students. This work is essential for student development, to become leaders at our institutions and in our fields with an aim to understand and dismantle systemic injustices.


_Instructions for contributing to this resource can be found in Chapter \@ref(contribute)._


